---
title: "Logistic Model Plots & Tables"
subtitle: "CXR Language Diagnostics"
author: "Lasse Hyldig Hansen"
date: "2023-04-19"
output: 
  html_document:
    toc: true
---

## Packages

```{r}
library(tidyverse)
library(lme4)
library(gtsummary)
library(ggrepel)
library(scales)
```

## Loading Data 

```{r}
df_for_model = read_csv("../topic_model_dataset.csv")
df_hier = read_csv("../hierarchical_structure_topic_model.csv")
df_lung_attr_map = read_csv("../lung_attribute_mapping.csv")
```

### Making sure there is a column to join on 

```{r}
df_hier$topic = df_hier$level3
```

### Joinging topic hierarchy names and dataframe with diseases

```{r}
df_for_model3 = left_join(df_for_model, df_hier, by = "topic")
```

### Mapping lung regions to topics

```{r}
# Removing a few index columns

df_for_model3$...1.x = NULL 
df_for_model3$...1.y = NULL 
df_lung_attr_map$...1 = NULL
df_for_model3$topic_name = NULL 

# Joining the two dataframes 

df_lung_attr_map2 = left_join(df_lung_attr_map, df_for_model3, 
                              by = c("reason_clean", "disease_category", "patient_id", "StudyDateTime", "study_id"))

df_lung_attr_map3 = df_lung_attr_map2 %>% drop_na()
```

### Prepare data for model

#### Getting topic name in the right levels (by count)

```{r}
name3_count = df_for_model3 %>% 
              group_by(level3_names, level2_names) %>% 
              summarize(count = n())

colnames(name3_count) <- c("name", "level_2_name", "count")

name3_count %>% arrange(desc(count)) %>% dplyr::select(name)
```

#### Relevelling the level3_names column

```{r}
df_for_model3$level3_names = factor(df_for_model3$level3_names, levels = c(
                                                      "Pneumonia & Respiratory Symptoms",
                                                      "Interval Change",
                                                      "Pulmonary Edema",
                                                      "Stroke, Hemorrhage, Seizure",

                                                      "Chest & Abdominal Pain",
                                                      "Hypoxia and Oxygen Requirements",
                                                      "Acute Dyspnea",
                                                      "Atrial Fibrillation",
                                                      
                                                      "Tube Placement",
                                                      "PICC Line Placement",
                                                      "Pacemaker Lead Placement",
                                                      
                                                      "Pleural Effusion",
                                                      "Pancreatitis & Pancreatic Cancer",
                                                      "Esophageal Cancer",
                                                      "Infiltrate Evaluation",
                                                      
                                                      "Altered Mental Status",
                                                      "Fever",
                                                      "Weakness & Confusion",
                                                      "Dizziness Assessment"
                                                        ))
```

#### Doing the same for age decile and gender 

```{r}
df_for_model3$gender = factor(df_for_model3$gender, levels = c(
                                                         "F",
                                                         "M"
                                                        ))

df_for_model3$disease_category2 = ifelse(df_for_model3$disease_category == "fluid overload/heart failure", 0, 
                                ifelse(df_for_model3$disease_category == "copd/emphysema", 1, 
                                       
                                       NA
                                       ))
```

## Making logistic models

```{r}

model_data = df_for_model3 %>% dplyr::select(disease_category2, level3_names) %>% drop_na()

log_model = glm(disease_category2 ~ level3_names, 
                data = model_data,
                family = "binomial")
```


### Getting coefficients in dataframe

```{r}
df_logistic = as.data.frame(summary(log_model)$coefficients)

df_logistic$Coefficient <- rownames(df_logistic)


df_logistic = df_logistic %>% 
            mutate(
              Coefficient = str_replace_all(Coefficient, "level3_names", "")
            )

levels(model_data$level3_names)
```

```{r}
df_logistic$Group = c(rep("Pulmonary & Neurovascular Health", 4), 
                      rep("Respiratory & Cardiovascular Health", 4), 
                      rep("Catheter & Lead Placement", 3), 
                      rep("Thoracic Disorders", 4),
                      rep("Neurological Symptoms", 4))

df_logistic = df_logistic %>% 
              mutate(Coefficient = ifelse(Coefficient == "(Intercept)", 
                                          "Pneumonia & Respiratory Symptoms", 
                                          Coefficient ))

## Getting odds ratios 
df_logistic$Estimate = exp(df_logistic$Estimate)

df_logistic2 = df_logistic

df_logistic2$Group <- factor(df_logistic2$Group, levels = c("Pulmonary & Neurovascular Health",
                                                            "Respiratory & Cardiovascular Health",
                                                            "Catheter & Lead Placement", 
                                                            "Thoracic Disorders",
                                                            "Neurological Symptoms"))

df_logistic2$model_name = "Topic Model"

df_logistic2$Coefficient2 = factor(df_logistic2$Coefficient, levels = rev(c(
                                                      "Pneumonia & Respiratory Symptoms",
                                                      "Interval Change",
                                                      "Pulmonary Edema",
                                                      "Stroke, Hemorrhage, Seizure",

                                                      "Chest & Abdominal Pain",
                                                      "Hypoxia and Oxygen Requirements",
                                                      "Acute Dyspnea",
                                                      "Atrial Fibrillation",
                                                      
                                                      "Tube Placement",
                                                      "PICC Line Placement",
                                                      "Pacemaker Lead Placement",
                                                      
                                                      "Pleural Effusion",
                                                      "Pancreatitis & Pancreatic Cancer",
                                                      "Esophageal Cancer",
                                                      "Infiltrate Evaluation",
                                                      
                                                      "Altered Mental Status",
                                                      "Fever",
                                                      "Weakness & Confusion",
                                                      "Dizziness Assessment")))
                                                      
```


### Visualization 1
#### With count on each topic

```{r}

colnames(name3_count) <- c("Coefficient", "Level2", "Count")

df_logistic3 = left_join(df_logistic2, name3_count, by = "Coefficient")
  
p_no_gend_count = ggplot(df_logistic3, 
                         aes(x = Estimate, 
                             y = Coefficient2, 
                             xmin = Estimate - 1.96*`Std. Error`, 
                             xmax = Estimate + 1.96*`Std. Error`, 
                             color = model_name)) +
                          geom_point(size = 2, 
                                     shape = 23, 
                                     position = position_dodge(width=0)) +
                          geom_errorbarh(height = 0.2, 
                                         position=position_dodge(width=0)) +
                          scale_color_manual(values = c("#D55E00")) + 
                          geom_vline(xintercept = 1) +
                          labs(
                               x = "Odds Ratios",
                               y = "",
                               color = "Model") +
                          theme_minimal() +
                          theme(strip.text = element_text(size = 10, 
                                                          face = "bold", 
                                                          margin = margin(b = 10)),
                                legend.title = element_blank(),
                                axis.title = element_text(size = 9),
                                axis.text = element_text(size = 9),
                                axis.title.y = element_text(margin = margin(r = 0)),
                                legend.position = "none",
                                trip.text.y.left = element_blank(),
                                panel.spacing = unit(3, "lines"),
                                panel.spacing.y = unit(0.3, "cm"),
                                plot.margin = unit(c(1, 0.2, 1 , 0.5), 'lines'),
                                strip.background = element_rect(fill = "white", color = "black", size = 0.5)) +
                          facet_grid(Group ~ ., scales = "free", space = "free", switch = "y") +
                          scale_x_continuous(expand = c(0,0)) 

p_no_gend_count2 <- p_no_gend_count +
                      geom_text(aes(x = -Inf, y = Inf, label = Group, fontface = "bold"),
                                size = 3, color = "black",
                                hjust = 1,
                                vjust = 0.2,
                                show.legend = FALSE) +
                      geom_segment(data = df_logistic3 %>% filter(Group == "Neurological Symptoms"), 
                                   aes(x = 0.9, xend = 0.1, y = -0.1, yend = -0.1), 
                                   arrow = arrow(length = unit(0.2, "cm")), 
                                   linetype = "solid",
                                   color = "black") +
                      geom_segment(data = df_logistic3 %>% filter(Group == "Neurological Symptoms"),
                                   aes(x = 1.1, xend = 3.9, y = -0.1, yend = -0.1), 
                                   arrow = arrow(length = unit(0.2, "cm")), 
                                   linetype = "solid",
                                   color = "black") +
                      geom_text(data = df_logistic3 %>% filter(Group == "Neurological Symptoms"),
                                aes(x = 0.5, y = -0.9, label = "FO / HF"),
                                color = "black",
                                size = 3,
                                vjust = 0) +
                      geom_text(data = df_logistic3 %>% filter(Group == "Neurological Symptoms"),
                                aes(x = 2.5, y = -0.9, label = "Copd / Emphysema"),
                                color = "black",
                                size = 3,
                                vjust = 0) +
                      coord_cartesian(clip = "off") +
                      geom_text(data = df_logistic3,
                                aes(x = Estimate, y = Coefficient2, label = paste0("n = ", Count)),
                                color = "black",
                                size = 3,
                                hjust = 0.3,
                                vjust = -1.5)
```

#### Without count on each topic 

```{r}
p_no_gend = ggplot(df_logistic2, 
                   aes(x = Estimate, 
                       y = Coefficient2, 
                       xmin = Estimate - 1.96*`Std. Error`, 
                       xmax = Estimate + 1.96*`Std. Error`, 
                       color = model_name)) +
                  geom_point(size = 2, 
                             shape = 23, 
                             position=position_dodge(width=0)) +
                  geom_errorbarh(height = 0.2, 
                                 position=position_dodge(width=0)) +
                  scale_color_manual(values = c("#D55E00")) + 
                  geom_vline(xintercept = 1) +
                  labs(
                       x = "Odds Ratios",
                       y = "",
                       color = "Model") +
                  theme_minimal() +
                  theme(strip.text = element_text(size = 10, 
                                                  face = "bold", 
                                                  margin = margin(b = 10)),
                        legend.title = element_blank(),
                        axis.title = element_text(size = 9),
                        axis.text = element_text(size = 9),
                        axis.title.y = element_text(margin = margin(r = 0)),
                        legend.position = "none",
                        strip.text.y.left = element_blank(),
                        panel.spacing = unit(3, "lines"),
                        panel.spacing.y = unit(0.3, "cm"),
                        plot.margin = unit(c(1, 0.2, 1 , 0.5), 'lines'),
                        strip.background = element_rect(fill = "white", color = "black", size = 0.5)) +
                  facet_grid(Group ~ ., scales = "free", space = "free", switch = "y") +
                  scale_x_continuous(expand = c(0,0)) 

p_no_gend2 <- p_no_gend +
              geom_text(aes(x = -Inf, y = Inf, label = Group, fontface = "bold"),
                        size = 3, color = "black",
                        hjust = 1,
                        vjust = 0.2,
                        show.legend = FALSE) +
              geom_segment(data = df_logistic2 %>% filter(Group == "Neurological Symptoms"), 
                           aes(x = 0.9, xend = 0.1, y = -0.1, yend = -0.1), 
                           arrow = arrow(length = unit(0.2, "cm")), 
                           linetype = "solid",
                           color = "black") +
              geom_segment(data = df_logistic2 %>% filter(Group == "Neurological Symptoms"),
                           aes(x = 1.1, xend = 3.9, y = -0.1, yend = -0.1), 
                           arrow = arrow(length = unit(0.2, "cm")), 
                           linetype = "solid",
                           color = "black") +
              geom_text(data = df_logistic2 %>% filter(Group == "Neurological Symptoms"),
                        aes(x = 0.5, y = -0.9, label = "FO / HF"),
                        color = "black",
                        size = 3,
                        vjust = 0) +
              geom_text(data = df_logistic2 %>% filter(Group == "Neurological Symptoms"),
                        aes(x = 2.5, y = -0.9, label = "Copd / Emphysema"),
                        color = "black",
                        size = 3,
                        vjust = 0) +
              coord_cartesian(clip = "off")
```


## Making logistic model 2

```{r}

model_data_int = df_for_model3 %>% dplyr::select(disease_category2, gender, level3_names) %>% drop_na()

log_model_int2 = glm(disease_category2 ~ level3_names + level3_names:gender, 
                data = model_data_int,
                family = "binomial")
```

## Logistic regression visualization 2

### First adding coefficient values to dataframe

```{r}
df_logistic_int = as.data.frame(summary(log_model_int2)$coefficients)

df_logistic_int$Coefficient <- rownames(df_logistic_int)


df_logistic_int = df_logistic_int %>% 
            mutate(
              Coefficient = str_replace_all(Coefficient, "level3_names", "")

            )

df_logistic_int = df_logistic_int %>% 
            mutate(
              Coefficient = str_replace_all(Coefficient, ":genderM", ""))
```

### Then wrangling this dataframe to fit ggplot input format

```{r}
df_logistic_int = df_logistic_int %>% mutate(Coefficient = ifelse(Coefficient == "(Intercept)", "Pneumonia & Respiratory Symptoms", Coefficient )
                                             )
df_logistic_int$Group = rep(c(
                      rep("Pulmonary & Neurovascular Health", 4), 
                      rep("Respiratory & Cardiovascular Health", 4), 
                      rep("Catheter & Lead Placement", 3), 
                      rep("Thoracic Disorders", 4),
                      rep("Neurological Symptoms", 4)), 2)

df_logistic_int$Estimate = exp(df_logistic_int$Estimate)

# Getting odds ratios 

df_logistic_int2 = df_logistic_int

df_logistic_int2$Group <- factor(df_logistic_int2$Group, levels = c(
                                                            "Pulmonary & Neurovascular Health",
                                                            "Respiratory & Cardiovascular Health",
                                                            "Catheter & Lead Placement", 
                                                            "Thoracic Disorders",
                                                            "Neurological Symptoms"))

df_logistic_int2$model_name = c(rep("Females", 19), rep("Males", 19))


df_logistic_int2$Coefficient2 = factor(df_logistic_int2$Coefficient, levels = rev(c(
                                                      "Pneumonia & Respiratory Symptoms",
                                                      "Interval Change",
                                                      "Pulmonary Edema",
                                                      "Stroke, Hemorrhage, Seizure",

                                                      "Chest & Abdominal Pain",
                                                      "Hypoxia and Oxygen Requirements",
                                                      "Acute Dyspnea",
                                                      "Atrial Fibrillation",
                                                      
                                                      "Tube Placement",
                                                      "PICC Line Placement",
                                                      "Pacemaker Lead Placement",
                                                      
                                                      "Pleural Effusion",
                                                      "Pancreatitis & Pancreatic Cancer",
                                                      "Esophageal Cancer",
                                                      "Infiltrate Evaluation",
                                                      
                                                      "Altered Mental Status",
                                                      "Fever",
                                                      "Weakness & Confusion",
                                                      "Dizziness Assessment")))
```

### Visualization for Interaction model

```{r}
p_int_noc = ggplot(df_logistic_int2, 
                   aes(x = Estimate, 
                       y = Coefficient2, 
                       xmin = Estimate - 1.96*`Std. Error`, 
                       xmax = Estimate + 1.96*`Std. Error`, 
                       color = model_name)) +
  geom_point(size = 2, 
             shape = 23, 
             position=position_dodge(width=0.5)) +
  geom_errorbarh(height = 0.2, position=position_dodge(width=0.5)) +
  scale_color_manual(values = c("#D55E00", "#264653"),
                     limits = c("Females", "Males")) + 
  geom_vline(xintercept = 1) +
  labs(
       x = "Odds Ratios",
       y = "",
       color = "Model") +
  theme_minimal() +
  theme(strip.text = element_text(size = 10, face = "bold", margin = margin(b = 10)),
        legend.title = element_blank(),
        axis.text.y=element_blank(),
        axis.title = element_text(size = 9),
        axis.ticks.y=element_blank() ,
        axis.title.y = element_text(margin = margin(r = 0)),
        legend.text = element_text(size = 10)) +
  facet_grid(Group ~ ., scales = "free", space = "free", switch = "y") +
  theme(strip.text.y.left = element_blank(),
        panel.spacing = unit(3, "lines"),
        panel.spacing.y = unit(0.3, "cm"),
        legend.position = c(0.85, 0.85),
        plot.margin = unit(c(1, 0.2, 1 , 0), 'lines'),

        #plot.margin = unit(c(1, 1, 2, 1), "lines"),
        strip.background = element_rect(fill = "white", color = "black", size = 0.5)) +
    scale_x_continuous(expand = c(0,0)) 

p_int_noc2 <- p_int_noc +
              geom_segment(data = df_logistic_int2 %>% filter(Group == "Neurological Symptoms"), 
                           aes(x = 0.9, xend = -0.5, y = -0.1, yend = -0.1), 
                           arrow = arrow(length = unit(0.2, "cm")), 
                           linetype = "solid",
                           color = "black") +
              geom_segment(data = df_logistic_int2 %>% filter(Group == "Neurological Symptoms"),
                           aes(x = 1.1, xend = 5, y = -0.1, yend = -0.1), 
                           arrow = arrow(length = unit(0.2, "cm")), 
                           linetype = "solid",
                           color = "black") +
              geom_text(data = df_logistic_int2 %>% filter(Group == "Neurological Symptoms"),
                        aes(x = 0.5, y = -0.9, label = "FO / HF"),
                        color = "black",
                        size = 3,
                        vjust = 0) +
              geom_text(data = df_logistic_int2 %>% filter(Group == "Neurological Symptoms"),
                        aes(x = 2.5, y = -0.9, label = "Copd / Emphysema"),
                        color = "black",
                        size = 3,
                        vjust = 0) +
              coord_cartesian(clip = "off")
```
### Saving visualization

```{r}
library(ggpubr)

png(filename = "logistic_plot_together.png", width = 3000, height = 1624, units = "px", res = 300)

ggarrange(p_no_gend2, p_int_noc2, labels = c("A", "B"), ncol = 2)

dev.off()
```
## Making logistic model tables

### First we need to make two new logistic regressions where we chagne the names of the predictors

```{r}
model_data2 = model_data %>% rename("Topic" = "level3_names")

model_data_int2 = model_data_int %>% rename("Topic" = "level3_names",
                                    "Gender" = "gender")

log_model_int3 = glm(disease_category2 ~ Topic + Topic:Gender, 
                data = model_data_int2,
                family = "binomial")

log_model2 = glm(disease_category2 ~ Topic, 
                data = model_data2,
                family = "binomial")
```

### Then we can construct the tables with AIC and Deviance values

```{r}
tbl1 = log_model2 %>% 
  tbl_regression(exponentiate = T) %>% 
  add_glance_table(include = c(AIC, deviance)) %>% 
  modify_header(label = "**Variable**", p.value = "**p**")

tbl2 = log_model_int3 %>% 
  tbl_regression(exponentiate = T) %>% 
  add_glance_table(include = c(AIC, deviance)) %>% 
  modify_header(label = "**Variable**", p.value = "**p**")

table = 
  tbl_merge(list(tbl1, tbl2),
            tab_spanner = c("**Model Simple**", "**Model Gender**")) %>% 
  modify_table_body(~.x %>% arrange(row_type == "glance_statistic"))
  
```



